### 2010-11-02 report/report.tex
Edited report.

\section{Executive Summary}

We are using machine learning to design a gait for a quadruped
robot. The robot has an on-board computer, drivers for the motors, and
will have camera feedback. The code so far consists of the robot
class, optimization class, parameterized model, sine model, and camera
feedback.  Both the hardware and software are progressing on schedule.
Some promising gaits have been generated, and we anticipate a final
evaluation of the robot’s gait in November.

@@

We are using machine learning to design a gait for a quadraped robot
from Hod Lipson’s lab. We anticipate using speed and number of
failures as metrics for evaluation of the designed gait.

@@

The quadraped robot has an on-board computer running Linux. The lower
level drivers are in C and we are implementing the system in
Python. Feedback about distance travelled is currently input manually,
but we eventually plan to provide this via an Optitrack positioning
system.

@@

\subsection*{\code{Optimization} class}

\begin{itemize}
\item \emph{Team member:} Sarah.
\item \emph{Current implementation:} Creates a random neighbor by
  randomly choosing one parameter to adjust, and changing either
  completely randomly in neighbor(), or slightly in
  slightNeighbor(). Then evaluates this neighbor by running the robot
  with the newly chosen parameters. If this neighbor results in a
  longer distance walked then the previous best neighbor, we save this
  neighbor as the new best neighbor. We then repeat the whole process
  using the best neighbor as a base.
\item \emph{Future improvements:} Gradient descent.
\item \emph{Status:} Initial algorithm coded. Improved algorithm
  slightNeighbor() coded. Gradient descent algorithm to be completed
  by Sarah.
\end{itemize}

@@

\subsection*{\code{CameraFeedback} class and hardware}

\begin{itemize}
\item \emph{Team member:} Diana.
\item \emph{Current implementation:} No software, still configuring
  camera hardware.
\item \emph{Future improvements:} Write python wrapper class, get
  positional information from the Optitrack camera system to the program
\item \emph{Status:} 20\% complete, goal to have cameras working by October 8.
\end{itemize}

@@

After running our program and finding a good gait, we will then
evaluate our system in two ways: the time taken to walk a certain
distance and the number of failures (i.e. falling down, getting
stuck). Both of these evaluation metrics depend on the result of
running our program for many iterations. Neither have been
completed. The evaluation for our particular project is an ongoing
process, but we anticipate a final evaluation taking place
early-to-mid November. The evaluation process will be completed by
Jason, Sarah, and Diana.

@@

We are meeting our project timeline and are, in fact, slightly ahead
of schedule. We have read the relevant papers, gotten lab access, and
talked with the appropriate people to learn the background information
necessary for working with the robot. We learned how to make the robot
move and have implemented an initial parameter optimization algorithm,
which has worked better than we anticipated.

@@

Week 5 (10/11-10/17)  & Algorithm dev/testing &
\\ \hline

Week 6 (10/18-10/24)  & Algorithm dev/testing &
\\ \hline

Week 7 (10/25-10/31)  & Algorithm dev/testing, quantify/solidify current results for Code Review \#2 &
\\ \hline

Week 8 (11/1-11/7)    & Finish collecting results, begin writing & 11/2 Code Review \#2
\\ \hline

Week 9 (11/8-11/14)   & Finish collecting results, writing &
\\ \hline

@@

\begin{itemize}
\item \code{optimize.py}: Employs random hill-climbing to choose and
  evaluate the parameters of the robots’ motion, either by changing
  one parameter completely randomly, or changing one parameter
  slightly. Evaluates each neighbor using manually input distance
  walked.
\item \code{Robot.py}: Implements the \code{Robot} class, described in
  \secref{implement}.
\item \code{SineModel.py}: Implements a sine based motion model,
  described in \secref{implement}.
\item \code{Motion.py}: Motion helper functions.
\end{itemize}

>>>>

\section{Executive Summary}
% A few sentences summarizing each of the items below
We are using machine learning to design a gait for a quadruped
robot. The robot has an on-board computer, drivers for the motors, and
will have camera feedback. The code so far consists of the robot
class, optimization class, parameterized model, sine model, and camera
feedback.  Both the hardware and software are progressing on schedule.
Some promising gaits have been generated, and we anticipate a final
evaluation of the robot’s gait in November.

@@

We are using machine learning to design a gait for a quadraped robot
from Hod Lipson’s lab. The metric for evaluation of the designed gait
is speed.

@@

The quadraped robot has an on-board computer running Linux. The lower
level drivers are in C and we are implementing the system in
Python. Feedback about distance travelled is provided via a Wii remote.

@@

\subsection*{\code{Strategy} and \code{RunManager} class}

\begin{itemize}
\item \emph{Team member:} Jason and Sarah.
\item \emph{Current implementation:} The user has a choice between four
  different learning strategies: uniform random hill climbing, gaussian random
  hill climbing, and N-dimensional policy gradient algorithm descent.
  \begin{itemize} 
  \item \emph{Uniform random hill climbing:} Creates a random neighbor by
  randomly choosing one parameter to adjust, and changing either
  completely randomly in UniformStrategy(), or slightly in
  UniformSlightStrategy(). Then evaluates this neighbor by running the robot
  with the newly chosen parameters. If this neighbor results in a
  longer distance walked then the previous best neighbor, we save this
  neighbor as the new best neighbor. We then repeat the whole process
  using the best neighbor as a base.
  \item \emph{Gaussian random hill climbing} Creates a random neighbor byi
  changing each parameter randomly based on a normal distribution. Then
  evaluates this neighbor similarly to uniform random hill climbing.
  \item \emph{N-dimensional policy gradient descent} Estimates the policy
  gradient by evaluating \emph{t} randomly generated policies
  near an initial parameter vector. Then computes the average score 
  \end{itemize}
\item \emph{Future improvements:} Machine learning of objective function.
\item \emph{Status:} Described algorithms coded. Machine learning of objective
  function to be coded by Jason.
\end{itemize}

@@

\subsection*{\code{WiiTrackClient} and \code{WiiTrackServer} classes
 and hardware}

\begin{itemize}
\item \emph{Team member:} Jason and Diana.
\item \emph{Current implementation:} A wii remote keeps track of the
position of the robot by tracking an infrared light on the robot. 
There is a motion loop that uses own position...(Jason and Diana, write
more about this.
\item \emph{Status:} Complete.
\end{itemize}

@@

\begin{itemize}
\item After running our program and finding a good gait, we will then
evaluate our system by the distance walked in a certain amount
of time. This evaluation metric depend on the result of
running our program for many iterations. We have done 50 runs of 
3 different inital parameter vectors for random hill climbing, 
gaussian random hill climbing, and policy gradient descent.
The evaluation for our particular project is an ongoing
process, but we anticipate a final evaluation taking place
early-to-mid November. The evaluation process will be completed by
Jason, Sarah, and Diana.

\item We also coded \code{explore\_dimensions} to collect data for dimension
varying plots. We intend to do further explore this by running
\code{explore\_dimension} around a parameter that produces a medium-good gait.
\end{itemize}

@@

We are meeting our project timeline. We have developed two new algorithms,
gaussian hill climbing and policy gradient descent and tested all three of
our major algorithms on the robot. We have also quantified our current results. 
In the next month we hope to develop one more learning strategy, machine
learning of an objective function.

@@

Week 5 (10/11-10/17)  & \done{Algorithm dev/testing} &
\\ \hline

Week 6 (10/18-10/24)  & \done{Algorithm dev/testing} &
\\ \hline

Week 7 (10/25-10/31)  & \done{Algorithm dev/testing, quantify/solidify current results for Code Review \#2} &
\\ \hline

Week 8 (11/1-11/7)    & \done{Finish collecting results, begin writing} & 11/2 Code Review \#2
\\ \hline

Week 9 (11/8-11/14)   & Algorithm dev/testing &
\\ \hline

@@

\begin{itemize}
\item \code{optimize.py}: Determines a strategy to try and runs the robot
  with that strategy.
\item \code{RunManager.py}: Deals with all the details of running the robot,
  including choosing an initial parameter, running the robot multiple times, 
  tracking distance walked, and writing to the log file. Also includes the
  \code{explore\_dimensions} method.
\item \code{Strategy.py}: Contains all the different possible strategies, which
  will be passed as objects in \code{optimize.py}. 
\item \code{Robot.py}: Implements the \code{Robot} class, described in
  \secref{implement}.
\item \code{SineModel.py}: Implements a sine based motion model,
  described in \secref{implement}.
\item \code{Motion.py}: Motion helper functions.
\item \code{WiiTrackServer.py, WiiTrackClient.py}: ? Jason, write this.
\end{itemize}
